---
title: "SimpLin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SimpLin}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(SimpLin)
```


# Description

`SimpLin` is an R package for performing simple linear regression analysis. It provides estimated regression coefficients, corresponding standard errors and 95% confidence intervals, residuals, and predicted values as a list.

# Usage

```{r eval=FALSE, include=TRUE}
result <- SimpLinR(x, y)
```

# Arguements

- `x`: A numeric vector representing the independent variable.
- `y`: A numeric vector representing the dependent variable. It must have the same length as `x`.

# Examples 

This is a basic example that demonstrates how to use the `SimpLinR` function with simulated data:

```{r example}
# Simulated data
x <- 1:100
y <- 2 * x + rnorm(100, mean = 0, sd = 20)

# Running the simple linear regression
result <- SimpLinR(x, y)

# Viewing the results
print(result)
```